Should geophysicists use gravity anomaly or gravity disturbance?

### 2018-05-16 manuscript/letter.tex
Started working on section 4

Let $\mitbf{g}_{P}$ and $\mitbf{\gamma}_{P}$ be, respectively, the
gravity vector (corrected from non-gravitational effects due to vehicle
motion and time variations such as Earth tides, instrumental drift and
barometric pressure changes, for instance) and the normal gravity vector
at a point $P$.
In this case, the gravity vector $\mitbf{g}_{P}$ represents the
gradient of a scalar potential called \textit{gravity potential},
which is the sum of a scalar gravitational potential and a
scalar centrifugal potential.
Similarly, the normal gravity vector $\mitbf{\gamma}_{P}$ represents the
gradient of a scalar potential called \textit{normal potential},
which is also the sum of a scalar gravitational potential and a
scalar centrifugal potential.
By definition, the centrifugal part of the normal potential is equal
to that of the gravity potential.

The difference between $\mitbf{g}_{P}$ and $\mitbf{\gamma}_{P}$, at the same
point $P$, defines a quantity called \textit{gravity disturbance
vector}, which is given by:
\begin{equation}
\delta \mitbf{g}_{P} =
\mitbf{g}_{P} - \mitbf{\gamma}_{P} \: .
\label{eq:gravity-disturbance-vector}
\end{equation}
Because the centrifugal part of the normal gravity vector
is equal to the centrifugal component of the gravity vector,
the gravity disturbance vector $\delta \mitbf{g}_{P}$ represents
a purely gravitational effect caused by contrasts between the actual internal
density distribution of the Earth and the internal density
distribution of the normal Earth.
In applied geophysics, these density differences are generally
called \textit{anomalous masses} (e.g., \citeauthor{hammer1945},
\citeyear{hammer1945}; \citeauthor{lafehr1965}, \citeyear{lafehr1965}),
\textit{density anomalies} (e.g., \citeauthor{forsberg1984},
\citeyear{forsberg1984}) or \textit{gravity sources} (e.g.,
\citeauthor{blakely1996}, \citeyear{blakely1996}). Here, we opted for
using the last term.
Fig. \ref{fig:surfaces} illustrates the gravity vector
$\mitbf{g}_{P}$, normal gravity vector $\mitbf{\gamma}_{P}$ and
the gravity disturbance vector $\delta \mitbf{g}_{P}$ at a point $P$
located on the Earth's surface.

>>>>

Let $\mitbf{\gamma}_{P}$ and $\mitbf{g}_{P}$ and be, respectively,
the \textit{normal gravity vector} and the Earth's \textit{gravity vector}
(corrected from non-gravitational effects due to vehicle
motion and time variations such as Earth tides and instrumental drift),
both located at a point $P$.
In this case, the gravity vector $\mitbf{g}_{P}$ is the
gradient of the scalar \textit{gravity potential},
which is the sum of a gravitational potential and a centrifugal potential.
Similarly, the normal gravity vector $\mitbf{\gamma}_{P}$ is the
gradient of the scalar \textit{normal potential},
which is also the sum of a gravitational and a centrifugal potential.
By definition, the centrifugal part of
the normal potential and the gravity potential are equal.

The difference between $\mitbf{g}_{P}$ and $\mitbf{\gamma}_{P}$,
which we emphasize are located at the same point $P$,
is the \textit{gravity disturbance vector} (Fig. \ref{fig:surfaces}):

\begin{equation}
\delta \mitbf{g}_{P} =
\mitbf{g}_{P} - \mitbf{\gamma}_{P} \: .
\label{eq:gravity-disturbance-vector}
\end{equation}

Because the centrifugal parts of both the normal gravity vector
and the Earth's gravity vector are equal,
the gravity disturbance vector $\delta \mitbf{g}_{P}$
represents a purely gravitational effect.
As a consequence of the superposition principal \citep{blakely1996},
this effect is caused by contrasts between
the internal density distributions
of the actual Earth and the normal Earth.
In applied geophysics, these density differences are generally called
\textit{anomalous masses} \citep[e.g.,][]{hammer1945,lafehr1965},
\textit{density anomalies} \citep[e.g.,][]{forsberg1984},
or \textit{gravity sources} \citep[e.g.,][]{blakely1996}.
Here, we opted for using the last term.
